---
title: "This is the other document"
author: "Julia Idzikowska"
data: today 
format:
  html:
    self-contained: true
    toc: true
    toc-location: left
    toc-title: My content
    theme:
      light: minty
      dark: superhero
    frontszie: 32x
    lang: pl
execute: 
  echo: fenced
  message: true
  error: true
code-fold: true
code-summary: See this specific code
warning: false 
---

# Plots

Below you will find a plot.

```{r}
#| echo: false
dataset = read.csv("~/Desktop/QUARTO/NEW_Quarto_ARCA/data/dataset.csv")
```


```{r}
#| echo: true 
#| out-width: 75%
#| fig-align: center
#| fig-cap: A graph from `mtcars`
#| fig-cap-location: margin
#| label: fig-mtcars

library(ggplot2)
ggplot(dataset, 
       aes(x = flexibility, y = anxiety, color = mindfulness)) +
  geom_point()

```

@fig-mtcars illustrates a plot


```{r}
#| label: tbl-mtcars

library(DT)
datatable(mtcars)
```

@tbl-mtcars is a table.

# Linear model
This is a Linear Model:
$$y = /beta_0 +/beta_1 X + /varepsilon$$


```{r}
#| echo: true 
#| column: margin
#| fig-column: margin

ggplot(mtcars, 
       aes(hp, mpg, color = factor(am))) +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess") +
  theme(legend.position = 'bottom')

datatable(mtcars,
  options = list(pageLength = 3))

```

# Multiple plots

@fig-plotsModels illustrates differents plots. @fig-plotsModels-1 stands for a, @fig-plotsModels-2 represents b, @fig-plotsModels-3 is just simply c and you can find @fig-plotsModels-4 as d. 

```{r}
#| echo: true 
#| label: fig-plotsModels
#| column: screen-inset-shaded
#| layout-nrow: 2
#| layout-ncol: 2
#| fig-cap: "One dataset, different models" 
#| fig-subcap:
#|   - "The data"
#|   - "Polynomial"
#|   - "Linear Model"
#|   - "GLM with Poisson" 


ggplot(mtcars,
       aes(mpg, hp, size = gear)) +
  geom_point()

ggplot(mtcars,
       aes(mpg, hp, size = gear)) +
  geom_point() + 
  geom_smooth()

ggplot(mtcars,
       aes(mpg, hp, size = gear)) +
  geom_point() + 
  geom_smooth(method = "lm")
ggplot(mtcars,
       aes(mpg, hp, size = gear)) +
  geom_point() + 
  geom_smooth(method = "glm", method.args = list(family = "poisson"))

```

# Multiple tables 

@tbl-tables present 2 datasets: @tbl-tables-1 is car and @tbl-tables-2 is pressure

```{r}
#| label: tbl-tables
#| tbl-cap: "Datasets"
#| tbl-subcap: 
#|   - "Cars"
#|   - "Pressure"
#| layout-ncol: 2

library(knitr)

kable(head(cars))

kable(head(pressure))
```


![This is an image]()
